\documentclass[letterpaper,12pt]{moderncv}

%\usepackage[scale=0.75]{geometry}
\usepackage[hmargin=0.5in,vmargin=1.0in]{geometry}
\usepackage{fontspec}
\usepackage{graphicx}

\usepackage{lipsum}

\setmainfont[
	Ligatures=TeX,
	%Letters=UppercaseSmallCaps,
	%Numbers=OldStyle
]{Garamond Premier Pro}

\moderncvtheme{classic}

\definecolor{color1}{RGB}{0,53,128}
%\definecolor{color3}{RGB}{0,157,217}
%\definecolor{color2}{RGB}{0,157,217}
\name{Richard}{Drake}

\address{959 Renfrew Court}{Oshawa, Ontario, Canada}{L1J 6L2}
\phone[mobile]{905.442.3152}
\email{richard.drake@uoit.ca}
\social[github]{rdrake}
\subject{RE:  Faculty of Science - Computing Laboratory Technician - UOIT 13-390}

\newcommand{\ucsc}[1]{\oldstylenums{\textsc{\lowercase{#1}}}}

\begin{document}
	\makecvtitle
	
	\section{Summary of Qualifications}
		\cvitem{}{\listitemsymbol Experience administrating OS X Server, dozens of OS X and Windows client machines, and Linux and FreeBSD servers.}
		\cvitem{}{\listitemsymbol Familiarity with existing staff, faculty, and IT staff.}
		\cvitem{}{\listitemsymbol Successful development of laboratory manuals for \ucsc{CSCI 4100U} Mobile Devices.}
		\cvitem{}{\listitemsymbol Strength in analyzing, researching, organizing, and problem solving.}
	
	\section{Education}
		\cventry{2010--2013 (Expected)}{Master of Science in Computer Science}{\ucsc{UOIT}}{Oshawa, Ontario, Canada}{}{}
		\cventry{2006--2010}{Bachelor of Science (Honours) in Computing Science}{\ucsc{UOIT}}{Oshawa, Ontario, Canada}{}{}
	
	\section{Master Thesis}
		\cvitem{Title}{Towards a Concurrent Implementation of Keyword Search Over Relational Databases}
		\cvitem{Supervisor}{Dr.~Ken Q.~Pu}
		\cvitem{Description}{}
	
	\section{Experience}
		\cventry{2011--Present}{Volunteer Webmaster}{Oshawa N.A.S.C.~Soccer}{Oshawa, Ontario, Canada}{}{Initiated a project to migrate the user-facing website from a static to dynamic, database-driven, modern web application.  Utilized Python/Django, PostgreSQL, \ucsc{SCSS}, \ucsc{HTML5}.}
		\cventry{Summer 2009 \& Summer 2010}{Undergraduate Summer Research Award}{\ucsc{UOIT}}{Oshawa, Ontario, Canada}{}{Designed and developed laboratory materials for \ucsc{CSCI 4100U} Mobile Devices.  Initially targeted toward iOS, later investigated the addition of BlackBerry OS.  Set up and maintained lab equipment.}
		\cventry{2007--2010}{Sole Proprietor}{Richard Drake}{Oshawa, Ontario, Canada}{}{Developed several database-driven client applications used to manage a company's quality control system.  Technologies used included C\#/.NET, T-SQL, and Microsoft SQL Server.}
	
	\clearpage
	
	\section{Computer Skills}
		\cvitem{System Administration}{Experience administrating OS X, Linux, Windows, and FreeBSD}
		\cvitem{Programming Languages}{Strong programmer in Java, Python, Ruby, Objective-C, and \ucsc{UNIX} shell}
		\cvitem{Web Development}{Several production Django and Flask applications, \ucsc{HTML5}, JavaScript, \ucsc{SCSS}}
	
	\section{Teaching Experience}
		\cventry{2011--2013}{Mobile Devices (\ucsc{CSCI 4100U})}{Laboratory Instructor}{}{}{}
		\cventry{Winter 2012}{Introduction to Computer Science with Python (\ucsc{CSCI 1040U})}{Laboratory Instructor}{}{}{}
		\cventry{Winter 2011}{Introduction to Computer Science with C++ (\ucsc{CSCI 1030U})}{Laboratory Instructor}{}{}{}
		\cventry{Fall 2010}{Database Systems \& Concepts (\ucsc{CSCI 3030U})}{Tutorial Instructor \& Grader}{}{}{}
	
	%\nocite{*}
	%\bibliographystyle{plain}
	%\bibliography{publications}
	
	\section{References}
	    \cvitem{}{References available upon request.}
	
	\clearpage
	
	\recipient{Human Resources}{University of Ontario Institute of Technology\\2000 Simcoe Street North\\Oshawa, Ontario, Canada\\L1H 7K4}
	\date{\today}
	\opening{To Whom It May Concern,}
	\closing{Sincerely,}
	\enclosure[Attached]{curriculum vit\ae{}}
	
	\makelettertitle
	
	% Things to keep in mind while writing a cover letter:
	% 
	% Why are you writing this?
	% - Why do you want the job?
	% - Why are you excited about the job?
	% 
	% Why should they hire you?
	% - What do you bring that no one else can?
	% - Why should they care about meeting you?
	% 
	% What kind of follow-up will there be?
	% - How can they contact you?
	% - When will you call them if you haven't heard anything? (I suggest something like "I will call in one week to follow the progress of hiring for this position.")
	
	I am applying for the position of Computing Laboratory Technician in the Faculty of Science (competition \textbf{\ucsc{UOIT 13-390}}).
	
	I am a motivated, driven, and responsible individual who is excited about new technology and always trying out new technologies.  I am confident that my experience at \ucsc{UOIT} as a student and a teacher lets me both connect with the students who will be using the lab, and be an effective authority figure as a supervisor/administrator.
	
	I would appreciate an opportunity to further discuss my qualifications at your earliest convenience.  You may reach me via email at \makeatletter\emaillink{\@email}\makeatother, or by phone at \phonesdetails. Thank you for your time.
	
	%I believe I am unique in that I am intimately familiar with the curriculum, laboratory setup, as well as pain points.
	\makeletterclosing
\end{document}